### 2023-06-13 Article.Rmd
refacut abstract + discussions

---
title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
author: 
  - name          : "Tanase Tasențe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "tanase.tasente@365.univ-ovidius.ro"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Equal contribution"
      - "Conceptualization"
      - "Data curation"
      - "Investigation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2"
    role:
      - "Equal contribution"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Data curation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
  - name          : "Cristina Dana Popescu"
    affiliation   : "1"
    role:
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Professional proofreading"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania"
  - id            : "2"
    institution   : "University of Bucharest, Romania"
authornote: |
  Department of Administrative and Social Sciences
abstract: |
  This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public engagement across different platforms (Facebook, Instagram, Twitter, and YouTube). Our results indicate that messages with emotional resonance significantly boost public engagement levels, with the effects varying based on the specific platform. We further reveal a notable influence of both positive and negative emotional resonance on engagement, with the latter exerting a stronger impact. This research expands our understanding of engagement dynamics on different platforms, stressing the importance of tailored platform-specific strategies. The findings underscore the crucial role of social media in enhancing public involvement in policy dialogue and emphasize the need for public institutions to incorporate emotional resonance into their communication strategies, accounting for unique platform characteristics. These insights provide a foundation for future discussions and research into optimizing communication strategies within a multi-platform environment, which will shape the future of digital governance and public policymaking.
keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount         : "4067 words in text body 1034 words in reference section"
bibliography      : ["r-references.bib", "references.bib"]
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
documentclass     : "apa7"
classoption       : "man"
csl               : apa.csl
output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_docx
header-includes:
  - \usepackage{ragged2e}
---

@@

# Discussion
This investigation commenced with the aim of assessing the impact of citizen engagement on the European Commission's social media platforms by specifically evaluating the influence of emotionally resonant communications on public engagement levels. The discussion here explores the findings derived from the study and their implications, juxtaposing them against the extant body of research on social media engagement, public institutional communication, and the role of emotional resonance in these facets.

The first hypothesis (H1) was predicated on the notion that communications with emotional resonance would yield higher public engagement levels. The research findings provided empirical support to this hypothesis, demonstrating a significant association between emotionally resonant communications and amplified levels of public engagement. This echoes previous scholarly work emphasizing the role of emotional appeal in enhancing audience engagement on social media platforms (Dolan et al., 2016; Smith & Gallicano, 2015). However, our research contributes a new dimension by bringing these aspects into the realm of public institutions, specifically the European Commission.

Public institutions often struggle with perceived remoteness and disconnection from citizens. However, the advent of social media offers a new avenue for these institutions to reach out to their citizenry, thereby allowing them to foster greater trust and engagement. Our findings confirm that the integration of emotional resonance within these online communications could significantly enhance this engagement process, fostering a more meaningful and interactive dialogue between the institutions and citizens.

Our findings align with the theoretical underpinnings of the uses and gratifications theory, emphasizing that emotional resonance serves as a primary motivation for users to engage with social media content. Consequently, public institutions should incorporate emotionally resonant messages into their social media communications to meet these user motivations, thus promoting higher engagement levels. This reflects the findings of Dolan et al. (2016), who identified emotional resonance as a key motivator in user engagement behavior.

The second hypothesis (H2) postulated that the social media platform could exert an influence on the emotional resonance in public engagement. The findings of the study substantiated this claim, revealing that the type of social media platform indeed moderates the impact of emotional resonance on public engagement. This variability across platforms underscores the need for a more nuanced, platform-specific approach to communication strategies.

Such an approach resonates with the findings of @Voorveld2018 who noted the differential roles of different social media platforms in user engagement. Public institutions, therefore, need to be mindful of these variations, ensuring that their communication strategies are tailored to the specific features, functionalities, and user behaviors of each platform to maximize the effectiveness of their emotionally resonant communications.

Our third hypothesis (H3) proposed that the social media platform could moderate the effect of emotional resonance on public engagement. This hypothesis was also validated by the study, underscoring the pivotal role that the choice of the social media platform plays in shaping public engagement levels. Each platform presents unique attributes and user behaviors, influencing the extent to which emotional resonance can stimulate public engagement.

This finding also converges with the research conducted by @Voorveld2018, which asserted the differentiating impact of platform type on social media engagement. Hence, the insights derived from our study reinforce the need for public institutions to strategically consider their choice of social media platform, factoring in the distinctive characteristics of each platform and their corresponding audience base to optimize their emotionally resonant communications.

A particularly interesting revelation was the relative impact of positive and negative emotional resonance on engagement levels. Both types of emotional resonance were found to amplify engagement levels, yet negative emotional resonance appeared to exert a stronger influence. This suggests that audiences may be more inclined to engage with messages that evoke negative emotions. Public institutions must carefully navigate this complex terrain, ensuring that their communications strike a delicate balance between positive and negative emotional resonance, taking into consideration the potential risks and rewards of each approach.

In sum, this study provides a wealth of empirical evidence to support the significance of emotional resonance in amplifying citizen engagement on the social media platforms of public institutions. It is a clarion call for public organizations to strategically incorporate emotional resonance into their communications, thereby leveraging this engagement driver to foster a more interactive, engaging dialogue with their audiences. Further, it highlights the pivotal role of platform choice, emphasizing the need to take into account the unique attributes and audiences of each platform in formulating and executing effective communication strategies.

However, despite its contributions, this study is not without its limitations. Future research should delve deeper into the intricate relationship between emotional resonance and public engagement, examining potential moderating factors such as the type of communication, audience demographics, or the cultural context. Additionally, further studies could evaluate the differential impact of positive and negative emotional resonance, providing a more nuanced understanding of how these contrasting types of emotional appeal influence public engagement. The role of individual social media platforms and their unique features in shaping emotional resonance could also be explored in more detail, providing insights into how public institutions can optimize their platform-specific strategies.

This research offers a critical springboard for public institutions to understand and leverage emotional resonance in their social media communications, thereby unlocking new opportunities for more effective and engaging citizen interactions. As public institutions continue to navigate the digital landscape, they must take these findings into account, recognizing the crucial role of emotional resonance in social media communications as well as the importance of adopting a platform-specific approach. The benefits of doing so will not only enhance public engagement but also foster a stronger, more trustful relationship between public institutions and their audiences.

>>>>

---
title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
shorttitle        : "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
author: 
  - name          : "Tanase Tasențe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "tanase.tasente@365.univ-ovidius.ro"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Equal contribution"
      - "Conceptualization"
      - "Data curation"
      - "Investigation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1,2"
    role:
      - "Equal contribution"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Data curation"
      - "Formal analysis"
      - "Resources"
      - "Software"
      - "Visualization"
  - name          : "Cristina Dana Popescu"
    affiliation   : "1"
    role:
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
      - "Professional proofreading"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania"
  - id            : "2"
    institution   : "University of Bucharest, Romania"
authornote: |
  Department of Administrative and Social Sciences
abstract: |
 This study investigates the role of emotional resonance in social media communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform digital governance environment.

keywords          : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount         : "4067 words in text body 1034 words in reference section"
bibliography      : ["r-references.bib", "references.bib"]
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
documentclass     : "apa7"
classoption       : "man"
csl               : apa.csl
output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_docx
header-includes:
  - \usepackage{ragged2e}
---

@@

# Discussion
The present investigation embarked on a quest to explore public engagement across various social media platforms utilized by the European Commission, with an emphasis on the impact of emotional resonance within content. The role of social media in public institutions' communication strategies is pivotal [@Smith2015], necessitating a deep understanding of engagement dynamics.

The data supports our first hypothesis (H1), suggesting that communications rich in emotional resonance, whether of positive or negative valence, are correlated with enhanced public engagement. However, the ability of emotional resonance to elucidate engagement levels is negligible (0.16%). This corroborates the complex nature of engagement behaviours expounded in scholarly literature [@Dolan2016; @Dragseth2020; @Mirbagheri2019] and points towards the necessity for further examination of supplementary factors influencing public engagement.

Our second hypothesis (H2) posited the influence of the social media platform choice on the effect of emotional resonance on public engagement. The empirical evidence supports this, suggesting that different platforms may cater to varied user expectations and norms. These findings align with prior research that demonstrated platform-specific fluctuations in engagement patterns [@Voorveld2018], underscoring the need for the European Commission to acknowledge heterogeneous engagement patterns and tailor their communications accordingly.

The third hypothesis (H3) asserted that the social media platform would moderate the impact of emotional resonance on public engagement. Our data confirmed this assumption, revealing a statistically significant moderating effect. This suggests that platforms may shape the way the public interacts with emotionally resonant messages, emphasizing the importance of customizing such communications to align with each platform's norms.

Despite these findings, the study is not without limitations. The low R^2 values in our regression models indicate that other unexamined variables might have significant effects on public engagement levels. Future research should persist in exploring these potential factors, acknowledging the complex and multifaceted nature of engagement behaviours.

Additionally, the scope of our research was limited to the European Commission's use of four major social media platforms. Further studies could explore other platforms or public institutions to see if the observed patterns hold. Also, while we focused on emotional resonance, other aspects of communication such as tone, complexity, and framing could be investigated in future research.

In conclusion, this study underscores the significance of emotional resonance and platform-specific norms in driving public engagement. It suggests that forming an emotional connection with the audience through posts could amplify engagement levels. By understanding these dynamics, public institutions like the European Commission can refine their social media strategies, enhance citizen engagement, and bolster the efficacy of their public communication. Despite the limitations, the study provides a valuable starting point for future research into the multifaceted world of social media engagement.
